Detecting threats of violence in YouTube comments

### 2016-03-03 submission.tex
Changed some of the tables

\begin{figure*}
\begin{verbatim}
timpa666
1    and i will kill every fucking muslim and arab!

@@

\end{verbatim}
\caption{Examples of comments from the data set.}
\label{fig:comments}
\end{figure*}

@@

\item \{$<$m, nsubj, i$>$, $<$root, root, m$>$, $<$scared, amod, fucking$>$, $<$m, acomp, scared$>$, $<$m, conj, kill$>$, $<$kill, dobj, them$>$, $<$kill, advmod, d$>$, $<$m, punct, :$>$ \}
\end{itemize}
Our lexical features are very specific and require the exact
combination of two lexical items in order to apply to a new instance.
Following \newcite{Jos:Pen:2009}, we therefore experiment with
generalization of features by backoff to a more general category,
e.g. from word form to lemma or PoS. A dependency triple over word
forms like $<$kill, dobj, them$>$ would thus be generalized to
$<$VERB, dobj, them$>$ using \emph{head-backoff} and $<$kill, dobj,
PRON$>$ using \emph{modifier-backoff}. We apply backoff to bigram,
trigram and dependency triple features.
\subsection{Development results}
Table \ref{tab:baseline} shows baseline results in terms of F-score
for bag-of, bigram and trigram templates over lexical features (word
form and lemma). The presented results constitute the best F-scores
after tuning, as discussed above. The
overall best result came from the logistic regression classifier with
the bag of word form feature set. Generally we see that feature sets
containing bag of lexical features in some form outperform the
$n$-gram feature sets.
The feature set we will use as a baseline in the next stage of our
experiments is bag of word forms. The feature set recieved an F-score
of $0.6123$, with a precision of $0.6777$ and a recall of $0.5585$,
using the MaxEnt classifier after tuning. We will also be
using only the MaxEnt classifier for the remainder of the
feature set experiments.
\begin{table*}
  \begin{center}
    \begin{tabular}{lrrr}
      \toprule

      & MaxEnt & SVM & Random Forest \\
      \midrule
      Bag of word forms & $\textbf{0.6123}$ & $\textbf{0.6068}$ & $\textbf{0.5918}$ \\ % SVM bag of words er bare best dersom word form + uPOS ikke er med i tabellen
      Bag of lemmas & $0.5902$ & $0.5982$ & $0.5856$ \\
      Bigrams & $0.4856$ & $0.4887$ & $0.4944$ \\
      Trigrams & $0.2776$ & $0.2856$ & $0.2859$ \\

      \bottomrule
      % Data fra firstPass i classify
      % Source/printFirstPassResults.py
    \end{tabular}
  \end{center}
  \caption{Results for baseline system; F-score for bag-of, bigram and trigram templates over lexical features (word form and lemma).}
  \label{tab:baseline}
\end{table*}

@@

\begin{table*}
  \begin{center}
    \begin{tabular}{lrr}
      \toprule

@@

    \end{tabular}
  \end{center}
  \caption{BoW is BoW \& dep triples, Best is BoW, BoL, n-grams \& dep triples}
  \label{tab:firsttriplebackoff}
\end{table*}

>>>>

\begin{figure}
\begin{verbatim}
timpa666
1    and i will kill every
     fucking muslim and arab!

@@

\end{verbatim}
\caption{Examples of comments from the data set.}
\label{fig:comments}
\end{figure}

@@

\item \{$<$m, nsubj, i$>$, $<$root, root, m$>$, $<$scared, amod, fucking$>$, $<$m, acomp, scared$>$, $<$m, conj, kill$>$, $<$kill, dobj, them$>$, $<$kill, advmod, d$>$, $<$m, punct, :$>$ \}
\end{itemize}
Our lexical features are very specific and require the exact
combination of two lexical items in order to apply to a new instance.
Following \newcite{Jos:Pen:2009}, we therefore experiment with
generalization of features by backoff to a more general category,
e.g. from word form to lemma or PoS. A dependency triple over word
forms like $<$kill, dobj, them$>$ would thus be generalized to
$<$VERB, dobj, them$>$ using \emph{head-backoff} and $<$kill, dobj,
PRON$>$ using \emph{modifier-backoff}. We apply backoff to bigram,
trigram and dependency triple features.
\subsection{Development results}
Table \ref{tab:baseline} shows baseline results in terms of F-score
for bag-of, bigram and trigram templates over lexical features (word
form and lemma). The presented results constitute the best F-scores
after tuning, as discussed above. The
overall best result came from the logistic regression classifier with
the bag of word form feature set. Generally we see that feature sets
containing bag of lexical features in some form outperform the
$n$-gram feature sets.
The feature set we will use as a baseline in the next stage of our
experiments is bag of word forms. The feature set recieved an F-score
of $0.6123$, with a precision of $0.6777$ and a recall of $0.5585$,
using the MaxEnt classifier after tuning. We will also be
using only the MaxEnt classifier for the remainder of the
feature set experiments.
\begin{table}
  \begin{center}
    \begin{tabular}{lrrr}
      \toprule

      & MaxEnt & SVM & RF \\
      \midrule
      Bag of word forms & $\textbf{0.6123}$ & $\textbf{0.6068}$ & $\textbf{0.5918}$ \\ % SVM bag of words er bare best dersom word form + uPOS ikke er med i tabellen
      Bag of lemmas & $0.5902$ & $0.5982$ & $0.5856$ \\
      Bigrams & $0.4856$ & $0.4887$ & $0.4944$ \\
      Trigrams & $0.2776$ & $0.2856$ & $0.2859$ \\

      \bottomrule
      % Data fra firstPass i classify
      % Source/printFirstPassResults.py
    \end{tabular}
  \end{center}
  \caption{Results for baseline system; F-score for bag-of, bigram and trigram templates over lexical features (word form and lemma). MaxEnt is the MaximumEntropy classifier, SVM is the support vector machine, and RF is the RandomForest classifier.}
  \label{tab:baseline}
\end{table}

@@

\begin{table}
  \begin{center}
    \begin{tabular}{lrr}
      \toprule

@@

    \end{tabular}
  \end{center}
  \caption{BoW is BoW \& dep triples, Best is BoW, BoL, n-grams \& dep triples}
  \label{tab:firsttriplebackoff}
\end{table}
